Generating Hubbard Model Solutions from Anderson Impurity Model Solutions

### 2021-08-06 notes.tex
added figures for Greens function

% !TEX TS-program = xelatex
\documentclass[12pt]{article}
\usepackage{amsthm,amsmath,amssymb,braket,graphicx,enumitem,booktabs,multirow,booktabs,tcolorbox,wrapfig,cancel,caption,fancyhdr,relsize,textpos,booktabs,tocbibind,titlesec}
\usepackage[margin=0.5in,bottom=0.6in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[hidelinks,pdfusetitle]{hyperref}
\usepackage[stable]{footmisc}
\renewcommand{\arraystretch}{1.9}
\setlength\delimitershortfall{-2pt}
%\pagestyle{fancy}
%\fancyhf{}
%\fancyfoot{}
%\fancyhead[L]{\nouppercase\leftmark}    
%\fancyhead[R]{\thepage}    
%\setlength{\headheight}{52pt}
\setcounter{tocdepth}{1}
\DeclareMathOperator{\sech}{sech}
\raggedbottom
\numberwithin{equation}{section}
\allowdisplaybreaks

@@

The local Hamiltonians look like
\begin{equation}\begin{aligned}
	H^A_{i,i_j} = -t^A\sum_{\sigma}\left(c^\dagger_{i\sigma}c_{i_j\sigma} + \text{h.c.}\right) + U^A\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}
\end{aligned}\end{equation}
We havent transformed the Anderson parameters \(U^A, t^A\) to the Hubbard parameters yet. The sum of all local Hamiltonians for a particular site \(i\) then gives the total Hamiltonian for that site:
\begin{equation}\begin{aligned}
	H^A_{i} = \sum_{j\in\left[1,w\right]}H^H_{i,i_j} = \sum_{\sigma\atop{j \in \text{N.N. of }i}}-t^A\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + w U^A\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}
\end{aligned}\end{equation}
If we now sum over all the lattice sites and take the average of all the Hamiltonians (\(Nw\) in number), we get
\begin{equation}\begin{aligned}
	H^H = \frac{1}{Nw}\sum_{i=1}^N H^H_{i} = -\frac{2}{Nw}t^A\sum_{\sigma\atop{\left<ij \right>}}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + \frac{1}{N}U^A\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}
\end{aligned}\end{equation}
The factor of 2 in front of \(t^A\) appears because each nearest neighbour pair \(\left<i,j \right>\) is counted twice, once when \(d\to i\) and again when \(d \to j\). Comparing with the actual Hubbard model, we can guess the following transformations for the model paramters:
\begin{equation}\begin{aligned}
	\frac{2}{Nw}t^A \to t^H, && \frac{1}{N}U^A \to U^H
\end{aligned}\end{equation}
For the dimer versions, we had \(N=2, w=1\) and if we substitute these values into the transformations we recover the transformations we had discovered that worked for the dimer. The Hubbard Hamiltonian can thus be obtained from the Anderson molecule using the following equation:
\begin{equation}\begin{aligned}
	H^H\left(t^H, U^H\right)  = \frac{1}{Nw}\sum_{\left<i,j\right>}\left[H^A\left(d \to i, z \to j\right) + H^A\left(d \to j, z \to i\right)\right]_{t^A \to \frac{Nw}{2}t^H \atop{U^A \to N U^H}}
\end{aligned}\end{equation}
The combination that is being summed over,
\begin{equation}\begin{aligned}
	H^A\left(d \to i, z \to j\right) + H^A\left(d \to j, z \to i\right)
\end{aligned}\end{equation}
is actually a Hubbard dimer Hamiltonian.
\begin{equation}\begin{aligned}
	&H^D(U^D, t^D) \equiv -t^D\sum_\sigma\left( c^\dagger_{0\sigma}c_{1\sigma} + \text{h.c.} \right) + U^D\left( \tau_{0 \uparrow}\tau_{0 \downarrow} + \tau_{1 \uparrow}\tau_{1 \downarrow}\right)\\
	&H^A\left(d \to i, z \to j\right) + H^A\left(d \to j, z \to i\right) = -2t^A\sum_\sigma\left( c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.} \right) + U^A\left( \tau_{i \uparrow}\tau_{i \downarrow} + \tau_{i \uparrow}\tau_{i \downarrow}\right)\\
	\implies &H^A\left(d \to i, z \to j\right) + H^A\left(d \to j, z \to i\right) = H^D(0 \to i, 1 \to j, t^D \to 2t^A, U^D \to U^A)
\end{aligned}\end{equation}
The tiling can thus be actually done in terms of Hubbard dimers:
\begin{equation}\begin{aligned}
	H^H\left(t^H, U^H\right)  = \frac{1}{Nw}\sum_{\left<i,j\right>}\left[H^D\left(1 \to i, 2 \to j\right)\right]_{t^D \to Nwt^H \atop{U^A \to N U^H}}
\end{aligned}\end{equation}
For reasons that will become apparent later, we will scale the internal Hubbard dimer by half, pulling out a two:
\begin{equation}\begin{aligned}
	\label{H_tiled}
	H^H\left(t^H, U^H\right)  = \frac{2}{Nw}\sum_{\left<i,j\right>}\left[H^D\left(1 \to i, 2 \to j\right)\right]_{t^D \to \frac{1}{2}Nwt^H \atop{U^D \to \frac{1}{2}N U^H}}
\end{aligned}\end{equation}

@@

@@

>>>>

% !TEX TS-program = xelatex
\documentclass[12pt]{article}
\usepackage{amsthm,amsmath,amssymb,braket,graphicx,enumitem,booktabs,multirow,booktabs,tcolorbox,wrapfig,cancel,caption,fancyhdr,relsize,textpos,booktabs,tocbibind,titlesec}
\usepackage[margin=0.5in,bottom=0.6in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[hidelinks,pdfusetitle]{hyperref}
\renewcommand{\arraystretch}{1.9}
\setlength\delimitershortfall{-2pt}
\setcounter{tocdepth}{1}
\DeclareMathOperator{\sech}{sech}
\raggedbottom
\numberwithin{equation}{section}
\allowdisplaybreaks

@@

The local Hamiltonians look like
	H^A_{i,i_j} = -t^A\sum_{\sigma}\left(c^\dagger_{i\sigma}c_{i_j\sigma} + \text{h.c.}\right) + U^A\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}
We havent transformed the Anderson parameters \(U^A, t^A\) to the Hubbard parameters yet. The sum of all local Hamiltonians for a particular site \(i\) then gives the total Hamiltonian for that site:
	H^A_{i} = \sum_{j\in\left[1,w\right]}H^H_{i,i_j} = \sum_{\sigma\atop{j \in \text{N.N. of }i}}-t^A\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + w U^A\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}
If we now sum over all the lattice sites and take the average of all the Hamiltonians (\(Nw\) in number), we get
	H^H = \frac{1}{Nw}\sum_{i=1}^N H^H_{i} = -\frac{2}{Nw}t^A\sum_{\sigma\atop{\left<ij \right>}}\left(c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.}\right) + \frac{1}{N}U^A\hat \tau_{i \uparrow}\hat \tau_{i \downarrow}
The factor of 2 in front of \(t^A\) appears because each nearest neighbour pair \(\left<i,j \right>\) is counted twice, once when \(d\to i\) and again when \(d \to j\). Comparing with the actual Hubbard model, we can guess the following transformations for the model paramters:
	\frac{2}{Nw}t^A \to t^H, && \frac{1}{N}U^A \to U^H
For the dimer versions, we had \(N=2, w=1\) and if we substitute these values into the transformations we recover the transformations we had discovered that worked for the dimer. The Hubbard Hamiltonian can thus be obtained from the Anderson molecule using the following equation:
	H^H\left(t^H, U^H\right)  = \frac{1}{Nw}\sum_{\left<i,j\right>}\left[H^A\left(d \to i, z \to j\right) + H^A\left(d \to j, z \to i\right)\right]_{t^A \to \frac{Nw}{2}t^H \atop{U^A \to N U^H}}
The combination that is being summed over,
	H^A\left(d \to i, z \to j\right) + H^A\left(d \to j, z \to i\right)
is actually a Hubbard dimer Hamiltonian.
	&H^D(U^D, t^D) \equiv -t^D\sum_\sigma\left( c^\dagger_{0\sigma}c_{1\sigma} + \text{h.c.} \right) + U^D\left( \tau_{0 \uparrow}\tau_{0 \downarrow} + \tau_{1 \uparrow}\tau_{1 \downarrow}\right)\\
	&H^A\left(d \to i, z \to j\right) + H^A\left(d \to j, z \to i\right) = -2t^A\sum_\sigma\left( c^\dagger_{i\sigma}c_{j\sigma} + \text{h.c.} \right) + U^A\left( \tau_{i \uparrow}\tau_{i \downarrow} + \tau_{i \uparrow}\tau_{i \downarrow}\right)\\
	\implies &H^A\left(d \to i, z \to j\right) + H^A\left(d \to j, z \to i\right) = H^D(0 \to i, 1 \to j, t^D \to 2t^A, U^D \to U^A)
The tiling can thus be actually done in terms of Hubbard dimers:
	H^H\left(t^H, U^H\right)  = \frac{1}{Nw}\sum_{\left<i,j\right>}\left[H^D\left(1 \to i, 2 \to j\right)\right]_{t^D \to Nwt^H \atop{U^A \to N U^H}}
Since the total number of nearest neighbour pairs is $\frac{Nw}{2}$, we want the prefactor to be the same. We will scale the internal Hubbard dimer by half, pulling out a two:
	\label{H_tiled}
	H^H\left(t^H, U^H\right)  = \frac{2}{Nw}\sum_{\left<i,j\right>}\left[H^D\left(1 \to i, 2 \to j\right)\right]_{t^D \to \frac{1}{2}Nwt^H \atop{U^D \to \frac{1}{2}N U^H}}
From this representation of the full Hubbard model, it is clear that symmetrizing the Anderson molecules by translating them throughout the lattice has restored translational invariance, and generated correlations on all sites (as compared to just on the impurity site). This also takes care of the problem that the spectrum of the Anderson molecule and Hubbard dimer are different for the $N=1$ or $N=3$ sectors: By translating the Anderson molecule suitably, we have recovered the correct spectrum in all sectors.

@@

	\label{local_gf}

@@

\begin{figure}[htpb!]
	\centering
	\hspace*{\fill}
	\includegraphics[width=0.7\textwidth]{./lattice.png}
	\hspace*{\fill}
	\caption{\textit{Left:} Part of the lattice that is picked out by the Greens function on the LHS of eq.~\ref{local_gf}. \textit{Right:} Hamiltonian whose Greens functions appear on the right hand side of same equation. The two submodels are identical.}
	\label{fig:}
\end{figure}
\\\\
